Supermartingales and Termination Analysis of Statistical PCF

### 2020-09-03 probabilisticProgrammingMartingales.tex
Fix typos

For any term $N$ which is not a value, there is a unique environment $E$ and redex $R$ such that $N = E[R]$. The position of the hole in $E$ is equal to $\cbv(N)$, so that $N|\cbv(N) = R$, as the cases in the definition of $\cbv$ match the cases in the definition of environments. If $R \new \tsample$, let $R'$ be the result of reducing $R$ (which is equal in both versions of the semantics), then $E[R'] = N[R' / \cbv(N)]$ therefore $\red(N,s) = (E[R'],s)$ and $(N,s) \Rightarrow_{\cbv} (E[R'],s)$. The distribution of next terms, conditional on the previous term, in the case that that previous term reduces deterministically, is therefore equal for $\red$ and $\Rightarrow_{\cbv}$.

@@

In any case, the distribution of reduction sequences after $n+1$ steps, conditional on the reduction sequence after $n$ steps, as defined by $\Rightarrow_\cbv$ and by $\red$, is equal, any by the inductive hypothesis the distributions after $n$ steps are equal, therefore by integrating over the reduction sequence up to step $n$, the distributions on reduction sequences up to step $n+1$ are equal.

>>>>

For any term $N$ which is not a value, there is a unique environment $E$ and redex $R$ such that $N = E[R]$. The position of the hole in $E$ is equal to $\cbv(N)$, so that $N|\cbv(N) = R$, as the cases in the definition of $\cbv$ match the cases in the definition of environments. If $R \neq \tsample$, let $R'$ be the result of reducing $R$ (which is equal in both versions of the semantics), then $E[R'] = N[R' / \cbv(N)]$ therefore $\red(N,s) = (E[R'],s)$ and $(N,s) \Rightarrow_{\cbv} (E[R'],s)$. The distribution of next terms, conditional on the previous term, in the case that that previous term reduces deterministically, is therefore equal for $\red$ and $\Rightarrow_{\cbv}$.

@@

In any case, the distribution of reduction sequences after $n+1$ steps, conditional on the reduction sequence after $n$ steps, as defined by $\Rightarrow_{\cbv}$ and by $\red$, is equal, any by the inductive hypothesis the distributions after $n$ steps are equal, therefore by integrating over the reduction sequence up to step $n$, the distributions on reduction sequences up to step $n+1$ are equal.
